%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Deedy - One Page Two Column Resume
% LaTeX Template
% Version 1.1 (30/4/2014)
%
% Original author:
% Debarghya Das (http://debarghyadas.com)
%
% Original repository:
% https://github.com/deedydas/Deedy-Resume
%
% IMPORTANT: THIS TEMPLATE NEEDS TO BE COMPILED WITH XeLaTeX
%
% This template uses several fonts not included with Windows/Linux by
% default. If you get compilation errors saying a font is missing, find the line
% on which the font is used and either change it to a font included with your
% operating system or comment the line out to use the default font.
% 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% 
% TODO:
% 1. Integrate biber/bibtex for article citation under publications.
% 2. Figure out a smoother way for the document to flow onto the next page.
% 3. Add styling information for a "Projects/Hacks" section.
% 4. Add location/address information
% 5. Merge OpenFont and MacFonts as a single sty with options.
% 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% CHANGELOG:
% v1.1:
% 1. Fixed several compilation bugs with \renewcommand
% 2. Got Open-source fonts (Windows/Linux support)
% 3. Added Last Updated
% 4. Move Title styling into .sty
% 5. Commented .sty file.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% Known Issues:
% 1. Overflows onto second page if any column's contents are more than the
% vertical limit
% 2. Hacky space on the first bullet point on the second column.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass[]{deedy-resume-openfont}


\begin{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     LAST UPDATED DATE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\lastupdated

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     TITLE NAME
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


\namesection{Timothy}{Kelly}{ 3900 Flying Gulch Drive, \#2, Holt, MI 48842 \\
\href{mailto:tj.kelly0795@gmail.com}{tj.kelly0795@gmail.com} | 517.414.2813
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN ONE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{minipage}[t]{0.33\textwidth} 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EDUCATION
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Education} 

\subsection{Michigan State University}
\descript{BS in Computer Science}
\descript{Minor in Mathematics}
College of Engineering \\
Honors College \\
Dean's List (All Semesters) \\
\location{Graduated May 2018 | East Lansing, MI \\ Cum. GPA: 3.95}
\sectionsep

\subsection{Jackson College}
\descript{High School Dual Enrollment}
\location{Fall 2013-Spring 2014 | Jackson, MI}
Dean's List (All Semesters) \\
\location{ Cum. GPA: 4.0}
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     LINKS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Links} 
Github:// \href{https://github.com/timjkelly}{\custombold{timjkelly}} \\
Github:// \href{https://github.com/tjkkelly}{\custombold{tjkkelly}} \\
LinkedIn://  \href{https://www.linkedin.com/in/tjkkelly}{\custombold{tjkkelly}}
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     COURSEWORK
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Coursework}

\subsection{Undergraduate}
MSU Capstone Experience \\
Introduction to Python \& C++ \\
Algorithm Engineering \& Data Structures \\
Computer Organization \& Architecture \\
Unix Tools and Scripting \\
Software Design \& OOP \\
Operating Systems \& Compilers \\
Computer Networks \& Security \\
Abstract Algebra \& Number Theory \\
Linear Algebra \& Real Analysis

\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     SKILLS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Skills}
\subsection{General}
Leadership \textbullet{}
Written \& Verbal Communication \textbullet{}
Agile \textbullet{} SAFe \textbullet{} TDD
\subsection{Programming}
Docker \textbullet{} Kubernetes \textbullet{}  
C\# \textbullet{}   C++ \textbullet{} C \textbullet{} Python \textbullet{} Java \textbullet{}
.Net \textbullet{} .Net Core \textbullet{} 
.Net Standard  \textbullet{} .Net CLI \textbullet{} 
ASP .Net Core \textbullet{} EF Core \textbullet{} 
Azure \textbullet{} AWS \textbullet{} 
GitHub \textbullet{} Splunk \textbullet{} \LaTeX\ \textbullet{} Moq \textbullet{}
NodeJS \textbullet{} React \textbullet{}
Hardware and Software Trans-coding \textbullet{}
Unit/Integration Testing \textbullet{}
CI/CD

\\

\location{Tools:}
Visual Studio (Windows/Mac/Code) \textbullet{} JetBrains Rider \textbullet{} Vim \textbullet{} NetBeans \textbullet{}
Command Line (Unix/Windows) \textbullet{}
Azure (Portal/DevOps) \textbullet{} TeamCity 


\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN TWO
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\end{minipage} 
\hfill
\begin{minipage}[t]{0.66\textwidth} 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EXPERIENCE
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Experience}

\runsubsection{TechSmith Corp.}
\descript{| Cloud Platform Software Engineer }
\location{July 2018 – Present | Okemos, MI}
\vspace{\topsep} % Hacky fix for awkward extra vertical space
\begin{tightemize}
    \item Designed and implemented ASP .Net Core Web APIs.
    \item Created and configured continuous builds, unit tests, integration tests, and deployments in Azure DevOps for .Net Core Projects using Docker containers and Kubernetes. 
    \item Experimented with running hosted agents in Kubernetes to optimize running integration tests with reduced authentication overhead.
    \item Moved live services deployed in a non-RBAC enabled Kubernetes cluster to a secured cluster with RBAC.
    \item Upgrade and improve logging in live services to get better insight into live applications.
    \end{tightemize}
\sectionsep

\runsubsection{TechSmith Corp.}
\descript{| Software Engineering Intern }
\location{January 2016 – July 2018 | Okemos, MI}
\vspace{\topsep} % Hacky fix for awkward extra vertical space
\begin{tightemize}
    \item Replaced deprecated screen capturing APIs with Microsoft Media Foundation and DirectX APIs within a shared internal library used across several products.
    \item Assisted in designing and developing several new cloud micro-services. This included setting up the Web API controllers, repositories, databases, migrations, and secure configuration all in the latest .Net Core Frameworks and Entity Framework Core written in C\#. 
    \item All code was peer-reviewed, tested, approved, and deployed to production.  All new code was unit and integration tested where appropriate.
    \item Organized and led the summer Intern Breakout Sessions where no full-time employees were present. Required organizational and leadership skills.
    \item Worked on several teams with sizes ranging from 2-8 using SAFe and Agile management techniques. Required clear and effective communication with team, including remote members.
    
    \end{tightemize}
\sectionsep

\runsubsection{MSU Information Security}
\descript{| Student Security Analyst }
\location{May 2017 – August 2017 | East Lansing, MI}
\begin{tightemize}
    \item Used Splunk to continue development on a Security Information and Event Management model to monitor and alert network security events campus-wide.
    \item Generated searches, dashboards, and alerts from various log types to analyze network activity and anomalies.
    \item Set up proper deployments and version control using git in multiple production environments to keep servers in parity and allow for safe deployments with rollbacks.
\end{tightemize}
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     AWARDS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Awards} 
\begin{tabular}{rll}
2017	     & Finalist in Google Games by Google Inc. \\
2016	     & Finalist in Atomic Games by Atomic Object \\
\end{tabular}
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     SOCIETIES
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Societies} 

\begin{tabular}{rll}
2017   & National   & MSU's Association for Computing Machinery (ACM) Co-President \\
2016   &  National  & MSU's ACM Event and Sponsorship Coordinator \\
2016 	& top 12\%ile    & Tau Beta Pi Engineering Honor Society \\
2014   &  MSU   & Honors College \\
\end{tabular}
\sectionsep

\end{minipage} 
\end{document}